---
title: "Data Analysis with R language"
output: html_notebook
---

Table of contents:

1. Explanatory data analysis with libraries *dplyr*, *tidyr* and *stringr* \
  * Subsetting columns \
  * Subsetting rows \
  * Logical operators, Boole'an algebra, de Morgan laws \
  * Creating new columns (1 exercise) \
  * Handling missing values \
  * Text manipulation (3 exercises) \
  * Data aggregation (1 exercise) \
  * Pivot tables, long and wide data format \
  * Joining tables \
  
2. Data vizualization with library *ggplot2* \
  * single numerical variable \
  * single categorical variable \
  * pair of numerical variables \
  * pair of categorical variables \
  * numerical and categorical variable \
  * bubble charts (3 exercises) \
  * multiple plot on single panel (2 exercises).

Useful links: \
 - [dplyr cheatsheet](https://raw.githubusercontent.com/rstudio/cheatsheets/main/data-transformation.pdf) \
 - [tidyr cheatsheet](https://raw.githubusercontent.com/rstudio/cheatsheets/main/tidyr.pdf) \
 - [stringr cheatsheet](https://raw.githubusercontent.com/rstudio/cheatsheets/main/strings.pdf) \
 - [ggplot2 cheatsheet](https://raw.githubusercontent.com/rstudio/cheatsheets/main/data-visualization.pdf) \
 - [A. Kassambara - Guide to Create Beautiful Graphics in R](http://www.sthda.com/english/download/3-ebooks/5-guide-to-create-beautiful-graphics-in-r-book/).
 
[Color palletes](https://www.datanovia.com/en/blog/the-a-z-of-rcolorbrewer-palette/)
  
```{r}
if(!require('tidyverse')) install.packages('tidyverse')
library(tidyverse)
```

Dataset comes from [https://flixgem.com/](https://flixgem.com/) (version from 12th March 2021). Dataset includes info about 9425 movies and series available on Netflix.
```{r}
df = read.csv('netflix-dataset.csv', encoding = 'UTF-8')
df
```

## Exploratory data analsis with dplyr and tidyr

### Subsetting columns

We select column by their names using *select()*. We can also remove columns be preceeding its name with minus sign.
```{r}
df %>%
  select(Title, Runtime, IMDb.Score, Release.Date)
```

```{r}
df %>%
  select(-Netflix.Link, -IMDb.Link, -Image, -Poster, -TMDb.Trailer)
```

```{r}
df %>%
  select(c(1:3, 7:8))
```

```{r}
df %>%
  select(Title:Runtime)
```

Useful functions during selecting columns: \
 - *starts_with()* - select/remove columns which names begins with a given string \
 - *ends_with()* - select/remove columns which names end with a given string \
 - *contains()* - select/remove columns which names contains given string.
```{r}
df %>%
  select(starts_with('IMDb'))
```

```{r}
df %>%
  select(ends_with('Score'))
```

```{r}
df %>%
  select(contains('Date'))
```

With function *matches()* we can select or remove columns which names include given regular expression. Useful tool for building and testing regular expressions can be found here: [https://regex101.com/](https://regex101.com/).

```{r}
df %>%
  select(matches('^[a-z]{5,6}$'))
```

```{r}
df %>%
  select(-matches('\\.'))
```

Function *select()* always returns data frame, but sometimes we need a single column returned as a vector. It can be achieved with function *pull()*.
```{r}
df %>%
  select(IMDb.Score) %>%
  unlist()

# df %>%
#   select(IMDb.Score) %>%
#   unlist(use.names = FALSE)
```

```{r}
df %>%
  pull(IMDb.Score, Title)
```

```{r}
df %>%
  pull(IMDb.Score, Title)
```

### Filtering rows

We filter rows with function *filter()* and comparison operators *==*, *!=*, *>*, *>=*, *<*, *<=*, *between()*. 
```{r}
df %>%
  filter(Series.or.Movie == 'Series')
```

```{r}
df %>%
  filter(IMDb.Score > 8)
```

### Logical operators, Boole'an algebra, de Morgan laws

Logical operator *AND* we denote with symbol *&* \
 - *FALSE & FALSE = FALSE* \
 - *FALSE & TRUE = FALSE* \
 - *TRUE & FALSE = FALSE* \
 - *TRUE & TRUE = TRUE*
```{r}
df %>%
  filter(IMDb.Score >= 8 & Series.or.Movie == 'Series')
```

Logical operator *OR* we denote with symbol *|* \
 - *FALSE | FALSE = FALSE* \
 - *FALSE | TRUE = TRUE* \
 - *TRUE | FALSE = TRUE* \
 - *TRUE | TRUE = TRUE*
```{r}
df %>%
  filter(IMDb.Score >= 9 | IMDb.Votes < 1000)
```

De Morgan laws states then when entering with negation into bracket then OR and AND are being exchanged: \
*not (A & B) = (not A) |(not B)* \
*not (A | B) = (not A) & (not B)* \
```{r}
df %>%
  filter(!(IMDb.Score >= 9 | IMDb.Votes < 1000))
```

```{r}
df %>%
  filter(!(IMDb.Score >= 9) & !(IMDb.Votes < 1000))
```

### Creating new columns:

With function *mutate()* we can add new columns or overwrite existing ones.
```{r}
df %>%
  mutate(score_category = if_else(IMDb.Score >= 5, 'Good', 'Poor')) %>%
  select(Title, IMDb.Score, score_category)
```

```{r}
df = df %>%
  mutate(
    Release.Date = Release.Date %>% as.Date(format = '%m/%d/%Y')
    ,Netflix.Release.Date = Netflix.Release.Date %>% as.Date(format = '%m/%d/%Y')
  )
```

**EXERCISE 1:** What is the oldest movie directed by Woody Allena available on Netflix?
```{r}
df %>%
  filter(Director == 'Woody Allen') %>%
  filter(Release.Date == min(Release.Date))
  select(Title, Director, Release.Date)
```

When using *case_when()* we don't need to explicitly write mutually exclusive conditions. Function evaluation occurs just after it encounters first true set of conditions.
```{r}
df %>%
  mutate(score_category = case_when(
    IMDb.Score <= 2 ~ 'Very Poor'
    ,IMDb.Score <= 4 ~ 'Poor'
    ,IMDb.Score <= 6 ~ 'Medium'
    ,IMDb.Score <= 8 ~ 'Good'
    ,IMDb.Score <= 10 ~ 'Very Good'
    )) %>%
  select(Title, IMDb.Score, score_category)
```

Mathematical functions performed on each row we apply by precedding whole operation with *rowwise()* function.
```{r}
df %>%
  select(ends_with('Score'))
```

```{r}
df %>%
  mutate(avg_score = mean(c(IMDb.Score * 10
                            ,Hidden.Gem.Score * 10
                            ,Rotten.Tomatoes.Score
                            ,Metacritic.Score)
                          ,na.rm = TRUE) %>%
           round(2)) %>%
  select(Title, avg_score)
```

```{r}
df %>% 
  rowwise() %>%
  mutate(avg_score = mean(c(IMDb.Score * 10
                            ,Hidden.Gem.Score * 10
                            ,Rotten.Tomatoes.Score
                            ,Metacritic.Score)
                          ,na.rm = TRUE) %>%
           round(2)) #%>%
  # select(Title, avg_score)
```

By default, new columns created with *mutate()* are added at the end of the data frame. With *relocate()* we can change position of a particular column.
```{r}
df %>%
  mutate(Popularity = if_else(IMDb.Votes > quantile(IMDb.Votes, 0.90, na.rm = TRUE), 'High', 'Not High')) %>%
  relocate(Popularity, .after = Title)
```

We can rename columns with *rename()*.
```{r}
df %>%
  rename(
    Tytul = Title
    ,Gatunek = Genre
  )
```

```{r}
df %>%
  mutate(Tytul = Title) %>%
  select(-Title) %>%
  relocate(Tytul, .before = everything())
```


### Handling missing values

Library *tidyr* provides several handful of function for dealing with missing data: \
 - *drop_na()* - delete rows with missing values in selected columns \
 - *replace_na()* - replace missing values with constant value \
 - *fill()* - replace missing values with first or last non-missing value.

```{r}
sum(is.na(df$Hidden.Gem.Score))
```

```{r}
df %>%
  sapply(function(x) is.na(x) %>% sum())
```

```{r}
df %>%
  drop_na(Hidden.Gem.Score, Awards.Nominated.For)
```

```{r}
df %>%
  mutate(Hidden.Gem.Score = replace_na(Hidden.Gem.Score, median(Hidden.Gem.Score, na.rm = TRUE))) %>%
  sapply(function(x) is.na(x) %>% sum())
```

```{r}
df %>%
  replace_na(list(Hidden.Gem.Score = median(df$Hidden.Gem.Score, na.rm = TRUE))) %>%
  sapply(function(x) is.na(x) %>% sum())
```

### Text manipulation

Library *stringr* contains handful of useful function for string manipulation and regular expressions. Most of functions from this library beging with *str_*.

```{r}
str_
```

Question: What can be improved in the below code to maintain *tidyverse* syntax?
```{r}
gatunki = df %>%
  pull(Genre) %>%
  paste0(collapse = ', ') %>%
  str_extract_all('[A-Za-z]+') %>%
  unlist() %>%
  table() %>%
  as.data.frame()

gatunki %>%
  arrange(-Freq)
```

```{r}
df$Series.or.Movie %>% table()
```

```{r}
df %>%
  mutate(poland_available = str_detect(Country.Availability, 'Poland')) %>%
  filter(poland_available == TRUE) %>%
  pull(Title)
```

With function *separate()* we can split single column into several ones, and we can join multiple columns into a single one with function *unite()*.
```{r}
df %>%
  unite(
    col = 'Scores'
    ,c('Hidden.Gem.Score', 'IMDb.Score', 'Rotten.Tomatoes.Score', 'Metacritic.Score')
    ,sep = ', '
  ) %>%
  select(Title, Scores)
```

```{r}
arrange(select(filter(...)))

filter(...) %>%
  select() %>%
  arrange()
``` 

**EXERCISE 2:** What are the best three comedies available in Polish language?
```{r}
# EXERCISE 2 ----
df %>%
  filter(Genre %>%
           str_detect('Comedy')) %>%
  filter(Languages %>%
           str_detect('Polish')) %>%
  arrange(-IMDb.Score) %>%
  select(Title, IMDb.Score) %>%
  top_n(3)

```

**EXERCISE 4:** What are the most popular tags for series and movies available in Polish language?
```{r}
df %>%
  filter(Languages %>%
           str_detect('Polish')) %>%
  pull(Tags) %>%
  str_c(collapse = ',') %>%
  str_split(',') %>%
  table() %>%
  as.data.frame() %>%
  arrange(-Freq) %>%
  top_n(10)
```

### Data aggregation

With functions *group_by()* and *summarize()* we work on aggregated data.
```{r}
df %>%
  group_by(Runtime) %>%
  summarize(
    count = n()
    ,avg_imdb_score = mean(IMDb.Score, na.rm = TRUE) %>% round(2)
    ,avg_imdb_votes = mean(IMDb.Votes, na.rm = TRUE) %>% round(0)
    ,sum_awards = sum(Awards.Received, na.rm = TRUE)
  )
```

```{r}
df %>%
  group_by(Series.or.Movie, Runtime) %>%
  summarize(n = n()) %>%
  arrange(-n)
```

**EXERCISE 3:** For movies and series released in 2019 and 2020 what is the average time between its release date and appearance on Netflix?

```{r}
library(lubridate)

df %>%
  mutate(Year = year(Release.Date)) %>%
  filter(between(Year, 2019, 2020)) %>%
  mutate(Datediff = Netflix.Release.Date - Release.Date) %>%
  group_by(Year) %>%
  summarize(mean(Datediff) %>% round(0))
```

```{r}
library(lubridate)

df %>%
  pull(Release.Date) %>%
  .[1:5] %>%
  year()

year(df$Release.Date[1:5])

```

**EXERCISE 5:** What are average ratings of movies produced in different decades (i.e. 60s, 70s, 80s, 90s etc.)?
```{r}

```

### Pivot tables, long and wide data format

df in *wide* format: \
 - single individuals are represented by rows \
 - their attributes are represented by columns \
 - in each cell there is a value of a given attribute for a given individual.
 
df in *long* format: \
 - in first columns can can see individual key (which can be constructed from multiple columns) \
 - all the attributes are in single column \
 - all the values are in single column.

*Long* format is especially useful when creating plots with library *ggplot2*.

```{r}
df_pivot = df %>%
  select(Title, ends_with('Score'))
```

```{r}
df_pivot = df_pivot %>%
  pivot_longer(
    cols = 2:5
    ,names_to = 'Attribute'
    ,values_to = 'Value'
  )
```

```{r}
df_pivot = df_pivot %>%
  pivot_wider(
    id_cols = 1
    ,names_from = 'Attribute'
    ,values_from = 'Value'
  )
```

### Joining tables

```{r}
oceny_metacritic = df %>%
  select(Title, Metacritic.Score) %>%
  .[1:100,] %>%
  drop_na()

oceny_rotten_tomatoes = df %>%
  select(Title, Rotten.Tomatoes.Score) %>%
  .[1:100,] %>%
  drop_na()
```

We join tables by their respective keys, exactly how we do it in SQL.
```{r}
oceny_metacritic %>%
  left_join(oceny_rotten_tomatoes, by = c('Title' = 'Title'))
```

```{r}
oceny_metacritic %>%
  right_join(oceny_rotten_tomatoes, by = c('Title' = 'Title'))
```

```{r}
oceny_metacritic %>%
  inner_join(oceny_rotten_tomatoes, by = c('Title' = 'Title'))
```

```{r}
oceny_metacritic %>%
  full_join(oceny_rotten_tomatoes, by = c('Title' = 'Title'))
```

```{r}
oceny_metacritic %>%
  anti_join(oceny_rotten_tomatoes, by = c('Title' = 'Title'))
```

```{r}
oceny_rotten_tomatoes %>%
  anti_join(oceny_metacritic, by = c('Title' = 'Title'))
```

## Data vizualization with library ggplot2

```{r}
theme_set(theme_bw())
```

General rules for creating plots with *ggplot2*: \
 - as arguments to *ggplot()* function provide data frame and optionally axes *x*, *y* and parameters *shape*, *color*, *fill*, *group* \
 - add plot layers with functions starting with *geom_* or *stat_* \
 - modify plot by adding legends, titles, markers etc.
 
For quick data vizualization one can use function *qplot()*, which automatically picks plot type to the underlying data.

### Single numerical variable

```{r}
ggplot(df, aes(x = IMDb.Score)) +
  geom_histogram(color = 'blue', fill = 'red')

ggplot(df, aes(x = IMDb.Score)) +
  geom_histogram(aes(fill = Series.or.Movie), color = 'black', bins = 50) +
  labs(x = 'Rating', y = 'Count', title = 'Histogram of movie ratings', fill = 'Serie or movie') +
  theme(legend.position = 'bottom')
```

```{r}
ggplot(df, aes(x = IMDb.Score)) +
  geom_histogram(
    aes(y = ..density..)
    ,bins = 50
    ,color = 'black'
    ,fill = 'white'
  ) +
  geom_density(
    aes(color = Series.or.Movie)
    ,color = 'blue'
    ,fill = 'lightblue'
    ,alpha = 0.5
    ,size = 1
  ) +
  labs(title = 'Density of ratings')
```

### Single categorical variable

```{r}
if(!require('RColorBrewer')) install.packages('RColorBrewer')
library(RColorBrewer)
```

```{r}
table(df$Runtime)
```

```{r}
df = df %>%
  filter(Runtime != '')

ggplot(df, aes(x = Runtime)) +
  geom_bar(aes(fill = Runtime)) +
    scale_x_discrete(
    limits = c('< 30 minutes'
               ,'30-60 mins'
               ,'1-2 hour'
               ,'> 2 hrs')
    ,labels = function(x) str_wrap(x, width = 8)
  ) 

ggplot(df, aes(x = Runtime)) +
  geom_bar(aes(fill = Runtime))+
  scale_x_discrete(
    limits = c('< 30 minutes'
               ,'30-60 mins'
               ,'1-2 hour'
               ,'> 2 hrs')
    ,labels = function(x) str_wrap(x, width = 8)
  ) +
  theme(
    legend.position = 'none'
    ,axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1)
  ) +
  scale_fill_manual(values = brewer.pal(4, 'Accent'))

```

### Pair of numerical variables

```{r}
ggplot(df, aes(x = IMDb.Score, y = IMDb.Votes)) +
  geom_point(aes(color = Series.or.Movie)) +
  geom_smooth(method = 'loess') +
  theme(legend.position = c(0.5, 0.5))

ggplot(df, aes(x = IMDb.Score, y = IMDb.Votes)) +
  geom_point(aes(color = Series.or.Movie)) +
  geom_smooth(method = 'lm') +
  theme(legend.position = c(0.2, 0.8)) +
  xlim(c(5, 7.5)) +
  ylim(c(0, 5e5))
```

### Pair of categorical variables

aes(
 x, y, fill, color, shape, size
)

```{r}
ggplot(df, aes(x = Series.or.Movie, y = Runtime)) +
  geom_jitter(aes(color = Runtime, shape = Series.or.Movie)) +
  # theme(legend.position = 'none') +
  scale_y_discrete(
    limits = c('< 30 minutes'
               ,'30-60 mins'
               ,'1-2 hour'
               ,'> 2 hrs')
  ) +
  labs(title = 'Plot tile', subtitle = 'test', x ='', y = '', color = 'Legend title', shape = 'Legend 2')
```

### Numerical and categorical variable

```{r}
ggplot(df, aes(x = Series.or.Movie, y = IMDb.Score)) +
  geom_boxplot(
    aes(fill = Series.or.Movie)
    ,outlier.alpha = 0.25
  ) + 
  #   geom_text(
  #   data = medians
  #   ,aes(x = Series.or.Movie, y = m, label = m)
  #   ,color = 'blue'
  #   ,hjust = 7 
  # ) + 
  stat_boxplot(geom ='errorbar', position = 'dodge') +
  stat_summary(
    aes(ymax = ..y.., ymin = ..y..)
    ,fun = mean
    ,geom = 'errorbar'
    ,width = .75
    ,linetype = 'solid'
    ,position = 'dodge'
    ,color = 'white'
    ,size = 1
  ) +
  theme(legend.position = 'none')
```

### Bubble charts

```{r}
if(!require('ggrepel')) install.packages('ggrepel')
library(ggrepel)
```

```{r}
genres <- df %>% 
  select(Genre) %>% 
  unlist() %>% 
  strsplit(',') %>%
  unlist() %>% 
  trimws() %>% 
  table() %>% 
  as.data.frame()

genres <- data.frame(
  Genre = genres$.
  ,`Count` = genres$Freq
  ,`IMDb Score Average` = NA
  ,`IMDb Votes Average` = NA
)

for (i in 1:nrow(genres)) {
  genres$IMDb.Score.Average[i] <- df %>% 
    filter(str_detect(Genre, genres$Genre[i] %>%
                        as.character() %>% eval())) %>%
    select(IMDb.Score) %>% unlist() %>% mean(na.rm = TRUE)
  
  genres$IMDb.Votes.Average[i] <- df %>% 
    filter(str_detect(Genre, genres$Genre[i] %>%
                        as.character() %>% eval())) %>%
    select(IMDb.Votes) %>% unlist() %>% mean(na.rm = TRUE)
}

ggplot(genres, aes(IMDb.Score.Average, IMDb.Votes.Average, label = Genre)) +
  geom_point(aes(color = Genre, size = Count)) +
  geom_text_repel() +
  theme(legend.position = 'none')
```

**EXERCISE 6:** Create alike plot with actors starred in the best movies.
```{r}
actors <- df %>% 
  select(Actors) %>% 
  unlist() %>% 
  strsplit(',') %>%
  unlist() %>% 
  trimws() %>% 
  table() %>% 
  as.data.frame()

actors <- data.frame(
  Actor = actors$.
  ,`Count` = actors$Freq
  ,`IMDb Score Average` = NA
  ,`IMDb Votes Average` = NA
) %>%
  filter(Count > 15)

for (i in 1:nrow(actors)) {
  actors$IMDb.Score.Average[i] <- df %>% 
    filter(str_detect(Actors, actors$Actor[i] %>%
                        as.character() %>% eval())) %>%
    select(IMDb.Score) %>% unlist() %>% mean(na.rm = TRUE)
  
  actors$IMDb.Votes.Average[i] <- df %>% 
    filter(str_detect(Actors, actors$Actor[i] %>%
                        as.character() %>% eval())) %>%
    select(IMDb.Votes) %>% unlist() %>% mean(na.rm = TRUE)
}

ggplot(actors, aes(IMDb.Score.Average, IMDb.Votes.Average, label = Actor)) +
  geom_point(aes(color = Actor, size = Count)) +
  geom_text_repel() +
  theme(legend.position = 'none')
```

**EXERCISE 7:** Create alike plot to show in which years the best movies were created.

```{r}
prod_yr <- df %>% 
  mutate(Year = lubridate::year(Release.Date)) %>%
  select(Year, IMDb.Score, IMDb.Votes) %>%
  group_by(Year) %>%
  summarize(Count = n()
            ,IMDb.Score.Average = mean(IMDb.Score, na.rm = TRUE)
            ,IMDb.Votes.Average = mean(IMDb.Votes, na.rm = TRUE)) %>%
  ungroup()

ggplot(prod_yr, aes(IMDb.Score.Average, IMDb.Votes.Average, label = Year)) +
  geom_point(aes(color = Year, size = Count)) +
  geom_text_repel(max.overlaps = 5) +
  theme(legend.position = 'none')

ggplot(prod_yr %>%
         filter(Count >= 10)
       ,aes(IMDb.Score.Average, IMDb.Votes.Average, label = Year)) +
  geom_point(aes(color = Year, size = Count)) +
  geom_text_repel(max.overlaps = 10) +
  theme(legend.position = 'none')
```

**EXERCISE 8:** What are the most popular languages available on Netflix? Hist: use column chart.
```{r}
languages <- df %>% select(Languages) %>% unlist() %>% strsplit(',') %>%
  unlist() %>% trimws() %>% table() %>% as.data.frame() %>% filter(Freq >= 20 & Freq <= 5000)
colnames(languages) <- c('Language', 'Count')

ggplot(languages, aes(x = reorder(Language, -Count), y = Count)) +
  geom_col(aes(fill = -Count)) +
  labs(x = '', y = '') +
  theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1)
        ,legend.position = 'none')

```

### Multiple plot on single panel

```{r}
ggplot(df, aes(x = IMDb.Score)) +
  geom_histogram(
    aes(fill = Series.or.Movie)
    ,bins = 50
    ,color = 'black'
  ) +
  # facet_grid(.~ Series.or.Movie)
  # facet_grid(Series.or.Movie ~ .)
  # facet_grid(Runtime ~ Series.or.Movie, scales = 'free')
  # facet_wrap(vars(Series.or.Movie), ncol = 2)
  # facet_wrap(vars(Series.or.Movie), nrow = 2)
  facet_wrap(vars(Series.or.Movie, Runtime), ncol = 3, scales = 'free') +
  theme(legend.position = 'none')
```

**EXERCISE 9:** For series and movies create plot of rating from different portals (Hidden Gem, IMDb, Rotten Tomatoes, Metacritic). Hint: worth to unpivot data frame to *long* format.

```{r}
df %>%
  select(ends_with('Score')) %>%
  pivot_longer(
    cols = 1:4
    ,names_to = 'Variable'
    ,values_to = 'Value'
  ) %>%
  drop_na() %>%
  ggplot(aes(x = Variable, y = Value)) +
  geom_boxplot(aes(fill = Variable)) +
  facet_wrap(vars(Variable), scales = 'free') +
  theme(legend.position = 'none')
```

```{r}
if(!require('gridExtra')) install.packages('gridExtra')
library(gridExtra)
```

```{r}
p1 = ggplot(df, aes(x = IMDb.Score, y = IMDb.Votes, color = Series.or.Movie)) +
  geom_point() +
  theme(legend.position = c(0.3, 0.8))

p2 = ggplot(genres, aes(IMDb.Score.Average, IMDb.Votes.Average, label = Genre)) +
  geom_point(aes(color = Genre, size = Count)) +
  geom_text_repel() +
  theme(legend.position = 'none')

grid.arrange(p1, p2, ncol = 2)
```

**EXERCISE 10:** Which production houses are most productive and how was it changing during recent years?
```{r}
df %>%
  mutate(rel_year = Release.Date %>%
           lubridate::year()) %>%
  select(rel_year, Production.House) %>%
  filter(Production.House != '' & rel_year %>% between(2010, 2020)) %>%
  drop_na() %>%
  separate_rows(Production.House, sep = ', ') %>%
  group_by(rel_year, Production.House) %>%
  summarize(n = n()) %>%
  ungroup() %>%
  filter(n > 3) %>%
  ggplot(aes(x = as.factor(rel_year), y = n, label = Production.House)) +
  geom_point(aes(color = rel_year, size = n)) +
  geom_text_repel(max.overlaps = 10) +
  theme(legend.position = 'none')

```